Bee visitation, pollination service, and plant yield in commodity and hybrid seed canola

### 2023-01-23 Manuscript/manuscript_files/supplemental.tex
Worked on revisions

\begin{table}[h]
\caption{Summary of variables used in structural equation models.}
\centering
\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.77 & 3.77 & 0.48 & 1.79 & 5.02\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 3.58 & 3.64 & 0.46 & 2.40 & 4.49\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}
\end{table}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth,keepaspectratio=true]{both_beeInt_time.png}
    \caption[Visitation model intercepts over time]{HB and LCB visitation models used random intercepts to account for variation between fields as well as over time. There was little systematic variation in HB intercepts across time, or between commodity field locations (Grand Prairie and Lethbridge), but there was a slight systematic decrease in seed field LCB intercepts during 2015, indicating that visitation rates declined across the season (this was not seen during the 2016 field season).}
\end{figure}

\begin{table}[h]
\caption{Summary of variables used in structural equation models.}
\centering
\begin{tabular}{l|l|r|r|r|r|r}
\hline
Field Type & Variable & Mean & Median & SD & Min & Max\\
\hline
 & Number of hives & 14.80 & 0.00 & 17.03 & 0.00 & 40.00\\
\cline{2-7}
 & Distance to edge (m) & 137.48 & 20.00 & 195.02 & 1.00 & 500.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 10.31 & 0.00 & 28.80 & 0.00 & 218.18\\
\cline{2-7}
 & Flower density (m$^2$) & 470.33 & 448.00 & 231.32 & 52.00 & 1684.00\\
\cline{2-7}
 & Pollen per stigma & 293.33 & 155.00 & 385.04 & 0.00 & 3891.00\\
\cline{2-7}
 & Plant density (m$^2$) & 48.53 & 43.50 & 22.91 & 6 & 151\\
\cline{2-7}
 & Plant vegetative mass (g) & 18.15 & 14.32 & 14.07 & 0.77 & 107.66\\
\cline{2-7}
 & Plant seed mass (g) & 6.87 & 5.46 & 5.97 & 0.01 & 47.90\\
\cline{2-7}
 & Harvest index (g/g) & 0.38 & 0.37 & 0.16 & 0.00 & 1.89\\
\cline{2-7}
 & Flowers per plant & 196.09 & 156.50 & 150.96 & 13.00 & 1094.00\\
\cline{2-7}
 & Pods per plant & 143.15 & 112.00 & 114.64 & 5.00 & 892.00\\
\cline{2-7}
 & Seeds per pod & 22.96 & 23.60 & 4.97 & 4.60 & 35.40\\
\cline{2-7}
\multirow{-13}{*}{\raggedright\arraybackslash Commodity} & Seed size (mg) & 2.74 & 2.73 & 0.80 & 0.39 & 5.35\\
\cline{1-7}
 & Distance to edge (m) & 162.70 & 100.00 & 146.18 & 3.00 & 400.00\\
\cline{2-7}
 & Distance to LCB shelter (m) & 33.51 & 31.00 & 24.63 & 2.00 & 190.00\\
\cline{2-7}
 & HB visitation (hr$^{-1}$) & 112.79 & 24.00 & 187.30 & 0.00 & 1290.00\\
\cline{2-7}
 & LCB visitation (hr$^{-1}$) & 76.15 & 12.00 & 144.88 & 0.00 & 1272.00\\
\cline{2-7}
 & Bay Edge/Centre & 0.13 & 0.00 & 0.34 & 0.00 & 1.00\\
\cline{2-7}
 & Flower density (m$^2$) & 495.02 & 432.00 & 303.35 & 24.00 & 2686.40\\
\cline{2-7}
 & Pollen per stigma & 21.76 & 7.00 & 42.53 & 0.00 & 578.00\\
\cline{2-7}
 & Plant density (m$^2$) & 39.65 & 38.00 & 16.87 & 11 & 89\\
\cline{2-7}
 & Plant vegetative mass (g) & 30.32 & 25.19 & 21.16 & 1.18 & 144.32\\
\cline{2-7}
 & Plant seed mass (g) & 9.50 & 7.54 & 7.90 & 0.02 & 60.77\\
\cline{2-7}
 & Harvest index (g/g) & 0.32 & 0.33 & 0.15 & 0.00 & 1.21\\
\cline{2-7}
 & Flowers per plant & 461.32 & 362.50 & 326.59 & 26.00 & 2712.00\\
\cline{2-7}
 & Pods per plant & 299.41 & 244.50 & 207.68 & 10.00 & 1410.00\\
\cline{2-7}
 & Seeds per pod & 16.40 & 16.60 & 5.52 & 1.80 & 30.60\\
\cline{2-7}
\multirow{-15}{*}{\raggedright\arraybackslash Seed} & Seed size (mg) & 3.43 & 3.42 & 0.88 & 1.04 & 5.59\\
\hline
\end{tabular}
\end{table}
